Men and Women Both Prefer and Perceive Inaction as More Competent

### 2024-02-16 outputs/paper/paper.qmd
paper upload

---
title: "Men and Women Both Prefer and Perceive Inaction as More Competent" 
subtitle: "An Analysis of Preference and Perceived Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender"
author: 
- Francesca Ye 
- Sky Suh 
- Hari Lee Robledo
date: "today"
date-format: long
abstract: "This report investigates differences between gender and perceptions of action versus inaction agents from research conducted by Adrien et al. Focusing on preference and perceived competence this report graphed the frequencies of responses by gender in addition to statistical analysis. This report found there are no significant differences in preference and perceived competence by gender as both slightly leaned towards inaction for both estimands. Considering the larger field of moral judgment, this report indicates that gender does not seem to be a  strong influence on decision-making approaches as previously thought."
thanks: "Code and data from this analysis are available at: https://github.com/hari-lr/Preference-and-Perception-of-Decision-Making". Replication on Social Science Reproduction platform available at: https://doi.org/10.1525/collabra.74817
toc: true
number-sections: true
bibliography: references.bib
format: pdf
---

>>>>

---
title: "Men and Women Both Prefer and Perceive Inaction as More Competent" 
subtitle: "An Analysis of Preference and Perceived Competence of Actions and Inaction Agents in Risky Decisions Resulting in Negative Outcomes by Gender"
author: 
- Francesca Ye 
- Sky Suh 
- Hari Lee Robledo
date: "today"
date-format: long
abstract: "This report investigates differences between gender and perceptions of action versus inaction agents from research conducted by Adrien et al. Focusing on preference and perceived competence this report graphed the frequencies of responses by gender in addition to statistical analysis. This report found there are no significant differences in preference and perceived competence by gender as both slightly leaned towards inaction for both estimands. Considering the larger field of moral judgment, this report indicates that gender does not seem to be a  strong influence on decision-making approaches as previously thought."
thanks: "Code and data from this analysis are available at: https://github.com/hari-lr/Preference-and-Perception-of-Decision-Making. Replication on Social Science Reproduction platform available at: https://doi.org/10.1525/collabra.74817"
toc: true
number-sections: true
bibliography: references.bib
format: pdf
---
